Open archaeology, open source?

### 2023-10-13 analysis/_03-data_methodology.qmd
Fill in blanks in section 3

<!--
* open-archaeo
* GitHub API
* Indicate how much is on GitHub or elsewhere
  -->

<!-- TODO: snappier title? Maybe incorporating 'open-archaeo'? -->

Our study comprises an exploratory analysis of open-archaeo [@batist2023], a list of open source archaeological software and other digital resources.
As of right now it includes <!-- TODO: encode -->408 items, which are rendered for the web at [open-archaeo.info](open-archaeo.info).

@@

```{r data-oarch}
read_csv("https://github.com/zackbatist/open-archaeo/raw/2023-08-29/open-archaeo.csv") %>%
  mutate(category = na_if(category, "?")) ->
  oarch

# Extract clean repos from GitHub URLs
oarch %>%
  mutate(
    gh_repo = str_match(oarch$github, "^https://github.com/([\\w-\\.]+/[\\w-\\.]+)/?.*?$")[,2]
  ) ->
  oarch

@@

The data and analysis code are available in our research compendium on GitHub, which is also indexed on Zenodo. <!-- TODO: add hyperlinks to these resources -->

>>>>

```{r data-oarch}
read_csv("https://github.com/zackbatist/open-archaeo/raw/2023-08-29/open-archaeo.csv") |>
  mutate(category = na_if(category, "?")) ->
  oarch

# Extract clean repos from GitHub URLs
oarch |>
  mutate(
    gh_repo = str_match(oarch$github, "^https://github.com/([\\w-\\.]+/[\\w-\\.]+)/?.*?$")[,2]
  ) ->
  oarch

We present an exploratory analysis of open-archaeo [[open-archaeo.info](open-archaeo.info), @batist2023], a directory of `r nrow(oarch)` pieces of open source archaeological software and other digital resources.

@@

@@

The quantitative analyses and figures presented here were generated with `r version$version.string` (@Manual).
The full data and code is available in the compendium that accompanies this paper (@Compendium).
